Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-01-07 Master Thesis/synopsis.tex
Add reference to F.K. Schmidt
Remove wrong assertion

\begin{lemma}\label{lemma-spvd}
Let $K$ be a finitely generated field of dimension $2$. Then we have:
\begin{enumerate}[(i)]
\item $\operatorname{Spv}^{(2)}(K) = \operatorname{Spv}^{(2)}_\text{d}(K) = \operatorname{Spv}^{(2)}_\text{rd}(K)$
\item $\operatorname{Spv}^{(1)}(K) = \operatorname{Spv}^{(1)}_\text{d}(K)$
\end{enumerate}
\end{lemma}

\begin{proof}
\begin{enumerate}[(i)]
\item Let $v\in\operatorname{Spv}^{(2)}(K)\subset |\operatorname{Spv}(K)|$. By Lemma \ref{2.2-prepre} we have $\dim k(v) = 0$ and thus the equality of the dimension inequality in Lemma \ref{rank-dimension-inequality}. By Lemma \ref{dimension-equality} $\Gamma_v$ is a finitely generated abelian group of rank $2$, thus not a subgroup of $\mathbb{R}$, i.e. $\operatorname{rank}(v)> 1$. 
\item Let $v\in\operatorname{Spv}^{(1)}(K)$. If $\operatorname{rank}(v) = 0$, $v$ would be the trivial valuation with trivial value group $\Gamma_v = 0$ and rational rank $0$. \qedhere
\end{enumerate}
\end{proof}

@@

Let $g\in G_K$ and $\overline{v}\in\operatorname{Spv}_\text{d}^{(1)}(\overline{K})$. By Remark \ref{3.3} we have:
\[ \sigma(g)\sigma(\overline{v}) = \sigma(g\overline{v}) = \tau(g\overline{v}) = \tau(g)\tau(\overline{v}) = \tau(g) \sigma(\overline{v}) \]
Therefore $\sigma(g)^{-1}\tau(g)$ is contained in $G_{\overline{v}}$ for all $\overline{v}\in\operatorname{Spv}_\text{d}^{(1)}(\overline{K})$. By the Theorem of F.K. Schmidt we have $G_{\overline{v}_1}\cap G_{\overline{v}_2} = 1$ for $\overline{v}_1\neq\overline{v}_2$. Therefore, $\sigma(g) = \tau(g) = \varphi^{-1}g\varphi$ for all $g\in G_K$.

>>>>

@@

Let $g\in G_K$ and $\overline{v}\in\operatorname{Spv}_\text{d}^{(1)}(\overline{K})$. By Remark \ref{3.3} we have:
\[ \sigma(g)\sigma(\overline{v}) = \sigma(g\overline{v}) = \tau(g\overline{v}) = \tau(g)\tau(\overline{v}) = \tau(g) \sigma(\overline{v}) \]
Therefore $\sigma(g)^{-1}\tau(g)$ is contained in $G_{\overline{v}}$ for all $\overline{v}\in\operatorname{Spv}_\text{d}^{(1)}(\overline{K})$. By the Theorem of F.K. Schmidt \ref{theorem-fkschmidt} we have $G_{\overline{v}_1}\cap G_{\overline{v}_2} = 1$ for $\overline{v}_1\neq\overline{v}_2$. Therefore, $\sigma(g) = \tau(g) = \varphi^{-1}g\varphi$ for all $g\in G_K$.
